%%%
\acknowledgments
\par I sincerely thank my guide Prof. Sai Vinjanampathy for his valuable guidance and constant support through out the duration of the work. I have been extremely lucky to have
a supervisor who cared so much about my work, and who responded to my questions and queries so
promptly. I was greatly benefited by his his hands-on-teaching techniques. I gratefully acknowledge the valuable time he spent with me helping me learn various theoretical and computational aspects of my work by providing his valuable suggestions and encouragement throughout.
\par 
I would also wish to express my gratitude to Prof Soumya Bera, Prof Dibyendu Das, Prof Sumiran Pujari, Prof Suddhasatta Mahapatra for extended discussions and valuable suggestions which have contributed greatly to the improvement of my understanding of physics  and its communication.
\par 
I am also thankful to my labmates and colleagues who helped me a lot in various ways. Special thanks are due to Surender Kumar, Vikram Sharma, Dr. Noufal P. Jaseem, Soumava Palit, Adhip Pattanayak, Mrudul M.S, Irfana Neyaz,   Dr Rohit Singh and Sucharita Giri






\signature{\today}
%\signature[Indian Institute of Technology Bombay]{\today}
\begin{comment}
Post. Doc. Fellow who developed the idea of HHG due to de-
fects in solid. Ms. Irfana Neyaz and Ms. Sucharita Giri, whose academic
discussions and advice were so interesting and useful.
I would like to thank my dear friend and colleague, Jiban Kangsabanik, PhD
student  in our group, for all the
time and efforts they have put in to obtain successful results.
This section is for the acknowledgments. Please keep this brief and resist the temptation of writing flowery prose! Do include all those who helped you, e.g. other faculty/staff you consulted, colleagues who assisted etc.
\end{comment}
%========================================================================

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mainrep"
%%% End: 