\chapter{Literature Survey}
Mike ike ,CRAB, DCRAB, GOAt etc biblio stuff already present in mylit.bib
The bibliographic entries are to be kept in a file named
\verb|<something>.bib|. In this sample report we call it as
\verb|mylit.bib|. This file must be included without the \verb|.bib|
extension in the main file as: \verb|\bibliography{mylit}|.   Open the
file \verb|mylit.bib| to see the format in which the entries are
written. This is written in the Bib\TeX format. Most of the
bibliographic web pages (Scopus, ISI Web) and software (EndNote, etc)
allow you to export bibliographic entries in the Bib\TeX format.

Citations are referred in the text using \verb|\citet| command which produces citations as though they are part of the text.  In order to say
somebody did this work as a part of a line use:
\verb|\citet{Batzri1973}| have done extensive work on \ldots.  This will produce
\citet{Batzri1973} have done extensive work on \ldots. Alternately citations can appear in parenthesis.  
The command~\verb|\citep{Batzri1973}| is used to automatically put the
citations in parenthesis.  As an example consider the extensive work
done in the area of book writing \citep{Sackmann1995a,Boal2012}.

Conferences \citep{rich-mart92} or collection of work
\citep{Sackmann1995a} also have special entries.

It is also possible to cite thesis like this:
\citet{jariwala00,luding94} or just unpublished work from
\citet{SunHI03}. Some times there are unclassified bibliographic
entries which can be put under ``misc'' \citep{Smith99}.
\citep{Whatisqubit} 
\citep{Tejas_APS1} \citep{wiki:resonator}

Tejas commonly used ones
\citep{nielsen2004quantum}
\citep{gerry2005introductory} \citep{caneva2011chopped} \citet{PaolaMIT2012}
\citep{2006quant.ph.12095L} \cite{jcreviewshoreknight}
@article{jcreviewshoreknight,
author = {Shore, Bruce and Knight, P},
year = {2018},
month = {09},
pages = {},
title = {Topical review The Jaynes-Cummings model}
}
URL citation format
\verb| @online{Whatisqubit,|\\
\verb|  author = {Margaret Rouse},|\\
\verb|  title = {DEFINITION qubit},|\\
\verb|  year = 2005,|\\
\verb|  url     = |\\
\verb|{\url{https://whatis.techtarget.com/definition/qubit}},|\\
\verb|  urldate = {2018-08-15}|\\
\verb|}|
can use verbatim environment for large blocks of text rather than  
\begin{verbatim}
\verb| |
 MIT OCW citation bibtex entry
 
@online{key,
  author = {Alan Oppenheim},
  year = {2011},
  month = {Spring},
  title = {Digital Signal Processing},
  subtitle = {RES.6-008},
  url = {https://ocw.mit.edu},
  organization = {Massachusetts Institute of Technology: MIT OpenCourseWare},
  addendum = {License: Creative Commons BY-NC-SA}
}
\end{verbatim}
Alan Oppenheim. RES.6-008 Digital Signal Processing. Spring 2011. Massachusetts Institute of Technology: MIT OpenCourseWare, https://ocw.mit.edu. License: Creative Commons BY-NC-SA.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mainrep"
%%% End: 
